
\documentclass[reqno,11pt]{amsart}

%\usepackage{color,graphicx}
%\usepackage{mathrsfs,amsbsy}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage[mathscr]{eucal}
\usepackage{float}
\usepackage{mathrsfs}
\usepackage{multicol}
\usepackage[all,pdf]{xy}
\usepackage[a4paper,left=3cm,right=3cm]{geometry}
\usepackage{xcolor}
%\usepackage[notcite,notref]{showkeys}

% showkeys  make label explicit on the paper

\makeatletter
\@namedef{subjclassname@2010}{%
  \textup{2010} Mathematics Subject Classification}
\makeatother

\numberwithin{equation}{section}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{defn}[theorem]{Definition}
\newtheorem{ques}[theorem]{Question}
\newtheorem*{fact}{Facts}
\newtheorem{eg}[theorem]{Example}

\theoremstyle{plain}
\newtheorem{thmsub}{Theorem}[subsection]
\newtheorem{lemmasub}[thmsub]{Lemma}
\newtheorem{corollarysub}[thmsub]{Corollary}
\newtheorem{propositionsub}[thmsub]{Proposition}
\newtheorem{defnsub}[thmsub]{Definition}

\numberwithin{equation}{section}


\theoremstyle{remark}

\newtheorem{remark}[theorem]{Remark}
\newtheorem{remarks}{Remarks}
\newcommand*\widebar[1]{%
	\hbox{%
		\vbox{%
			\hrule height 0.5pt % The actual bar
			\kern0.6ex%         % Distance between bar and symbol
			\hbox{%
				\kern 0em%      % Shortening on the left side
				\ensuremath{#1}%
				\kern 0em%      % Shortening on the right side
			}%
		}%
	}%
}
%\renewcommand\thefootnote{\fnsymbol{footnote}}
%dont use number as footnote symbol, use this command to change

\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\dist}{dist}
\DeclareMathOperator{\vol}{vol}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\Img}{\operatorname{Im}}
\DeclareMathOperator{\Id}{\operatorname{Id}}
\DeclareMathOperator{\Rep}{\operatorname{Rep}}
\DeclareMathOperator{\Mod}{\operatorname{Mod}}
\DeclareMathOperator{\Hom}{\operatorname{Hom}}
\DeclareMathOperator{\Ext}{\operatorname{Ext}}
\DeclareMathOperator{\gldim}{\operatorname{gl.dim}}
\DeclareMathOperator{\projdim}{\operatorname{proj.dim}}
\DeclareMathOperator{\injdim}{\operatorname{inj.dim}}
\DeclareMathOperator{\dimv}{\operatorname{\underline{\mathbf{dim}}}}


\DeclareMathOperator{\Flagd}{\operatorname{Flag}_{\mathbf{d}}}
\DeclareMathOperator{\Flagdstr}{\operatorname{Flag}_{\mathbf{d},str}}
\newcommand{\Grr}{\operatorname{Gr}^{R}}
\newcommand{\Grq}{\operatorname{Gr}^{KQ}}
\newcommand{\Flag}[1]{\operatorname{Flag}_{\mathbf{#1}}}
\newcommand{\Flagstr}[1]{\operatorname{Flag}_{\mathbf{#1},str}}
\newcommand{\dimvec}[1]{\mathbf{#1}}
\newcommand{\ord}{\operatorname{ord}}
\newcommand{\orde}{\operatorname{ord}_e }
\begin{document}
\date{}

\title
{Affine paving of partial flag quiver variety}


\author{Xiaoxiang Zhou}
\address{School of Mathematical Sciences\\
University of Bonn\\
Bonn, 53115\\ Germany\\} 
\email{email:xx352229@mail.ustc.edu.cn}





\begin{abstract}
In this article, we establish an affine paving for partial flag quiver varieties when the quiver is of Dynkin type. By copying results in \cite[section 6]{irelli2019cell} word by word, the same problem for affine quiver reduced to the case where the representation is regular quasi-simple. The idea of the proof mainly comes from \cite{irelli2019cell}, and the result is a natural continuation of \cite{maksimau2019flag}.
\end{abstract}



\maketitle
\tableofcontents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Let $Q$ be a quiver of Dynkin or affine type(without loops), $X\in \Rep(Q)$ be an quiver representation.\footnote{We fix the base field $K=\mathbb{C}$ for convinience.} We are interested in three objects related to $X \in \Rep(Q)$:
\begin{equation*}
\begin{aligned}
&	\text{quiver Grassmannian} && \Grq(X)\colon = \left\{ M_1 \mid M_1 \subseteq X \right\}\\
&	\text{partial flag variety \textcolor{gray}{$d\geqslant 1$}} && \Flagd(X)\colon =\left\{ 0 \subseteq M_1 \subseteq \cdots M_d \subseteq X \right\}\\
&	\text{strict partial flag variety \textcolor{gray}{$d\geqslant 2$}} && \Flagdstr(X)\colon =\left\{ 0 \subseteq M_1 \subseteq \cdots M_d \subseteq X  \mid x.M_{i+1} \subseteq M_i\right\}\footnotemark\\
\end{aligned}
\end{equation*}
\footnotetext{for any $x \in Q_1, i \in \{2,\ldots ,d \} $.}

It's easy to see that $\Flag{1}(X)=\Grq(X)$. These geometrical objects can be divided into different pieces according to the dimension vectors of $M_1,\ldots,M_d$, and each piece have its own natural (complex/Zarisky) topology. It was proved in \cite{irelli2019cell} that $\Grq(X)$ have an affine paving, and in \cite{maksimau2019flag} that $\Flagd(X)$ have the same property when $Q$ is Dynkin quiver of type $A/E$. Here we go one step further, the results are concluded in the ???.

???Here is one table

The idea of proof is very simple: first, we view the partial flag quiver variety as the quiver Grassmannian of the more complicated quiver; then we establish the decomposition so that one may solve the problem by induction; finally we set a special way of decomposition for each indecomposable module so that we can avoid meeting the bad decomposition. These contents are in Section ???, accordingly.

Before the end of this section, let us see in one example how partial flag variety is viewed as quiver Grassmannian.

\begin{eg}
Let $Q\colon x \longrightarrow y \longleftarrow z \longrightarrow w$ be a quiver, and let $X\colon X_x \longrightarrow X_y \longleftarrow X_z \longrightarrow X_w$ be a quiver representation, then $\Flag{3}(X),\Flagstr{3}$ can be viewed as quiver Grassmannian in ???:

???[pictures here]


\end{eg}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Preliminary Facts}
Fix the quiver $Q$ ant the integer $d \geqslant 2$, we define the new bigger quiver $Q_{d},Q_{d,str}$ as follows:

\begin{itemize}
	\item The vertex set of $Q_d$(resp. $Q_{d,str}$) is defined as the Cartesian product of the vertex set of $Q$ and $\{1,\ldots,d\}$, i.e.
	$$v(Q_d)=v(Q_{d,str})=v(Q) \times \{1,\ldots,d\}$$
	\item  The arrows of $Q_d$(resp. $Q_{d,str}$) is defined as follows:
	\begin{itemize}
		\item for each $(i,r) \in v(Q) \times \{1,\ldots,d-1\}$, there is one arrow from $(i,r)$ to $(i,r+1)$;
		\item for each arrow $i \longrightarrow j$ in quiver $Q$:
		\begin{itemize}
			\item $Q_d$ case: there is one arrow from $(i,r)$ to $(j,r)$; \textcolor{gray}{(for any $r \in \{1,\ldots,d\}$)}
			\item $Q_{d,str}$ case: there is one arrow from $(i,r)$ to $(j,r-1)$; \textcolor{gray}{(for any $r \in \{1,\ldots,d-1\}$)}			
		\end{itemize}
	\end{itemize}
\end{itemize}
\begin{eg}
Here is the picture of new quiver:

???[pictures here]
\end{eg}

We define the ring 
$$R=??? or ???$$
and define the canonical map $\Phi:\Rep(Q) \longrightarrow \Mod(R) \textcolor{gray}{\subseteq \Rep(Q_d \text{ or } Q_{d,str})}$ as follows:
\begin{itemize}
\item $\left(\Phi(X)\right)_{(i,r)}:=X_i$;
\item $\left(\Phi(X)\right)_{(i,r) \rightarrow (i,r+1)}:=\Id_{X_i}$;
\item $\left(\Phi(X)\right)_{(i,r) \rightarrow (j,-)}:=X_{i \rightarrow j} \textcolor{gray}{ \quad(i \rightarrow j)}$;
\end{itemize}
For the module $T \in \Mod(R)$, we define $\Grr(T)\colon=\{T' \subseteq T \text{ as the submodule}  \}$.
\begin{proposition}
Fix the representation $X\in \Rep(Q)$, we have the isomorphism
$$\Flag{}(X)\cong \Grr(\Phi(X)).$$
\begin{proof}
The two side give us same amount of informations. Or, you can easily construct the bijection from $\Flag{}(X)$ to $\Grr(\Phi(X))$.
\end{proof}
\end{proposition}
\subsection{Ext-vanishing properties}
We would like to show some higher rank Extension group to be 0, which would be a key ingredient in the proof of the next section.

\begin{lemma}\label{lm:Extvan}
Let $M,N,X,S \in \Rep(Q)$, $V,W,T \in \Mod(R)$.
\begin{enumerate}[(1)]
	\item $\gldim R \leqslant 2$;\label{lm:gldim}
	\item The functor $\Phi:\Rep(Q) \longrightarrow \Mod(R)$ is exact;
	\item $\Phi$ maps projective module to projective module;\label{lm:toproj}
	\item $\Hom_{KQ}(M,N) \cong \Hom_{R}(\Phi(M),\Phi(N)),\quad\Ext^i_{KQ}(M,N) \cong \Ext^i_{R}(\Phi(M),\Phi(N))$;
	\item $\projdim \Phi(M) \leqslant 1, \injdim \Phi(M) \leqslant 1$;
	\item Suppose $V \subseteq \Phi(X), W \subseteq \Phi(S),$ then $\Ext^2_{R}(W,T)=0, \Ext^2_{R}(T,\Phi(X)/V)=0$.\label{lm:Ext2van}
\end{enumerate}
\end{lemma}
\begin{proof}
For (\ref{lm:gldim}), we just need to check minimal projective resolution of $S(i)$ in $\Mod(R)$; for (\ref{lm:toproj}), we reduced to the case of indecomposable projective modules. The rests are easy exercises of homological algebra.
\end{proof}
\subsection{How much do we understand the quiver representation?}
To understand the category $\Rep(Q)$, one should understand indecomposable modules(as well as their relations). This has almost been done in the Auslander-Reiten theory. For example, when the quiver $Q$ is of Dynkin type, then there are only finite ind rep(up to isomorphism) and each ind rep corresponds to the positive root of Dynkin diagram. One can compute the Auslander-Reiten quiver by knitting algorithm and get the structure of ind rep. Moreover, one can directly get Hom space between $M$ and $N$ by looking at nontrivial paths from $M$ to $N$\footnote{These paths may be linear dependent, so it's not too easy.}.

We will use the Auslander-Reiten quiver to find "good monomorphisms" in Section ???. For more informations about Auslander-Reiten theory, one can see ???.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Main Theorem}
   
   The following notations will be used throughout this article:
   %In the following sections, we always suppose that 
   \begin{itemize}
   		\item $X,Y,S,M,N \in \Rep(Q), V,U,W,T,T' \in \Mod(R)$;
   		\item we have the short exact sequence $\eta:0\longrightarrow X \longrightarrow Y \longrightarrow S \longrightarrow 0$, and $V \subseteq \Phi(X), U \subseteq \Phi(Y), W \subseteq \Phi(S)$;
   		\item $\dimvec{f},\dimvec{g}$ are dimension vectors of quiver $Q_d$ or $Q_{d,str}$. $\Grr_{\dimvec{f}}(T):= \{ T' \subseteq T \mid \dimv T'=\dimvec{f} \}$ is defined as the set of subrepresentations with dimension vector $\dimvec{f}$.
   \end{itemize}
We use 
\begin{equation*}
\begin{aligned}[]
	[M,N]^i:&=\dim_K \Ext^i_{KQ} (M,N),\qquad [M,N]:=\dim_K \Hom_{KQ} (M,N)\\
	[T,T']^i:&=\dim_K \Ext^i_R (T,T'),\qquad\hspace{0.5cm} [T,T']:=\dim_K \Hom_R (T,T')\\
	\left< T,T'\right>_R:&= \sum_{i=0}^{\infty} (-1)^i [T,T']^i \quad=[T,T']-[T,T']^1+[T,T']^2\\
	\left< \dimvec{f},\dimvec{g}\right>_R:&= \sum_{i \in v(R)} f_ig_i - \sum_{b \in a(R)} f_{s(b)}g_{t(b)}+ \sum_{c \in va(R)} f_{s(c)}g_{t(c)}
\end{aligned}
\end{equation*}
for the shorthand notation, where
\begin{equation*}
\begin{aligned}
	v(R):&= \{\text{vertices in quiver $KQ_d$ or $KQ_{d,str}$}\} \\
	a(R):&= \{\text{arrows in quiver $KQ_d$ or $KQ_{d,str}$}\} \\
	va(R):&= \{\text{"virtual arrows" in quiver $KQ_d$ or $KQ_{d,str}$}\} \\
\end{aligned}
\end{equation*}

???[pictures with caption "virtual arrow: can ne thought as the "face" of the quiver"]

Let $\eta: 0\longrightarrow X \stackrel{\iota}{\longrightarrow} Y \stackrel{\pi}{\longrightarrow} S \longrightarrow 0$ be a short exact sequence in $Rep(Q)$. Consider the canonical \textbf{non-continuous} map
$$\Psi: \Grr(\Phi(Y)) \longrightarrow \Grr(\Phi(X)) \times \Grr(\Phi(S)) \qquad U \longmapsto \left([\Phi(\iota)]^{-1}(U),[\Phi(\pi)](U)   \right)$$
and  $\Psi_{\dimvec{f},\dimvec{g}}$ is the map $\Psi$ restricted to the preimage of $\Grr_{\dimvec{f}}(\Phi(X)) \times \Grr_{\dimvec{g}}(\Phi(S))$.

The goal of this section is to prove the following theorems:
\begin{theorem}\label{thm:main1}
	When $\eta$ splits, $\Psi$ is surjective. Moreover, $\Psi_{\dimvec{f},\dimvec{g}}$ is a Zarisky-locally trivial affine bundle of rank $\left< \dimvec{g},\dimv \Phi(X) - \dimvec{f}\right>_R$.
\end{theorem}
\begin{theorem}[follows {\cite[Theorem 32]{irelli2019cell}}]\label{thm:main2}
	When $\eta$ does not split and $[S,X]^1=1$, 
	$$\Img \Psi_{\dimvec{f},\dimvec{g}} = \bigg(\Grr_{\dimvec{f}}(\Phi(X)) \times \Grr_{\dimvec{g}}(\Phi(S)) \bigg) \setminus \bigg(\Grr_{\dimvec{f}}(\Phi(X_S)) \times \Grr_{\dimvec{g}-\dimv \Phi(S^X)}\left(\Phi(S/S^X)\right) \bigg)$$
	where 
	\begin{equation*}
	\begin{aligned}
	X_S:&= \max \left\{ M \subseteq X \,\middle|\; [S,X/M ]^1=1 \right\} \subseteq X\\
	S^X:&= \max \left\{ M \subseteq S \,\middle|\; [M,X]^1=1 \right\} \subseteq S
	\end{aligned}
	\end{equation*}
Moreover, $\Psi_{\dimvec{f},\dimvec{g}}$ is a Zarisky-locally trivial affine bundle of rank $\left< \dimvec{g},\dimv \Phi(X) - \dimvec{f}\right>_R$ over $\Img \Psi_{\dimvec{f},\dimvec{g}}$.
\end{theorem}

We will spend the rest of the section proving this theorem. We decide the image as well as the fiber of $\Psi$ respectively.
\begin{lemma}[follows {\cite[Lemma 21]{irelli2019cell}}]
The element $(V,W) \in \Grr(\Phi(X)) \times \Grr(\Phi(S))$ lies in the image of $/\Psi$ iff the canonical map $\Ext^1(\Phi(S),\Phi(X)) \longrightarrow \Ext^1(W,\Phi(X)/V)$ maps $\eta$ to 0.
\end{lemma}
\begin{proof}
	This follows from the definition of the canonical map.
	
	[??? Picture $\pi'$]
\end{proof}
\begin{corollary}\label{cor:img1}
	When $\eta$ splits, $\Psi$ is surjective.
\end{corollary}
\begin{lemma}
	the canonical map $\Ext^1(\Phi(S),\Phi(X)) \longrightarrow \Ext^1(W,\Phi(X)/V)$ is surjective.
\end{lemma}
\begin{proof}
	By using the LES of Extension groups and the Lemma \ref{lm:Extvan}(\ref{lm:Ext2van}), the maps
	$$\Ext^1(\Phi(S),\Phi(X)) \longrightarrow \Ext^1(W,\Phi(X))\qquad \Ext^1(W,\Phi(X)) \longrightarrow \Ext^1(W,\Phi(X)/V)$$
	are both surjective. Thus the composition is also surjective.
\end{proof}
\begin{corollary}[]\label{cor:0or1}
	When $[S,X]^1=1$, then $[W,\Phi(X)/V]^1=0 \text{ or }1$.
	
	Suppose $\eta$ generates $\Ext^1(S,X)$, then 
	$$(V,W) \in \Img \Psi \iff [W,\Phi(X)/V]^1=0.$$
\end{corollary}

In the case where $\eta$ generates $\Ext^1(S,X)$, we want to describe $\Img \Psi$ more precisely. For this reason we need to introduce two new $R$-modules:
	\begin{equation*}
	\begin{aligned}
	\widetilde{X_S}:&= \max \left\{ V \subseteq \Phi(X) \,\middle|\; [\Phi(S),\Phi(X)/V ]^1=1 \right\} \subseteq \Phi(X)\\
	\widetilde{S^X}:&= \max \left\{ W \subseteq \Phi(S) \,\middle|\; [W,\Phi(X)]^1=1 \right\} \subseteq \Phi(S)
	\end{aligned}
	\end{equation*}
$\widetilde{X_S}$ and $\widetilde{S^X}$ are well-defined because of the following lemma:
\begin{lemma}[follows {\cite[Lemma 27]{irelli2019cell}}]

\begin{enumerate}[(i)]
	\item[] 
	\item Let $V,V' \subset \Phi(X)$ such that $[\Phi(S),\Phi(X)/V ]^1=[\Phi(S),\Phi(X)/V']^1=1 .$ Then $[\Phi(S),\Phi(X)/V+V' ]^1=1$.
	\item  Let $W,W' \subset \Phi(S)$ such that $[W,\Phi(X)]^1=[W',\Phi(X)]^1=1 .$ Then $[W\cap W',\Phi(X)]^1=1$.
\end{enumerate}
\end{lemma}
\begin{proof}
We only prove (i). (ii) is similar.

From the SES 
$$0 \longrightarrow \Phi(X)/V\cap V' \longrightarrow \Phi(X)/V \oplus \Phi(X)/V' \longrightarrow \Phi(X)/V+V' \longrightarrow 0,$$
we get the LES
???change the way of format
$$\cdots\longrightarrow \Ext^1(\Phi(S),\Phi(X)/V\cap V') \longrightarrow \Ext^1(\Phi(S),\Phi(X)/V) \oplus \Ext^1(\Phi(S),\Phi(X)/V') \longrightarrow \Ext^1(\Phi(S),\Phi(X)/V+V') \longrightarrow\cdots$$
By Corollary \ref{cor:0or1}, $[\Phi(S),\Phi(X)/V\cap V']^1\leqslant 1, \; [\Phi(S),\Phi(X)/V+V']^1\leqslant 1$, and this forces that $[\Phi(S),\Phi(X)/V+V']^1= 1$.
\end{proof}
\begin{lemma}[follows {\cite[Lemma 31(1)(2)]{irelli2019cell}}, and the proof is same]

Let $f:X \longrightarrow \tau S$ be a non-zero morphism, then $X_S=\ker (f)$; also, $\Phi(f): \Phi(X) \longrightarrow \Phi(\tau S)$ is a non-zero morphism, $\widetilde{X_S}=\ker (\Phi(f))$.
\end{lemma}
\begin{corollary}
	$\widetilde{X_S}=\Phi(X_S)$.\textcolor{gray}{(since $\widetilde{X_S}=\ker (\Phi(f))=\Phi(\ker(f))=\Phi(X_S)$)}
\end{corollary}
By the similar argument, one can show that $\widetilde{S^X}=\Phi(S^X)$.
\begin{lemma}[follows {\cite[Lemma 31(6)]{irelli2019cell}}]
Given $V \subseteq \Phi(X)$ and $W \subseteq \Phi(S)$, we have 
$$[W,\Phi(X)/V]^1=0 \iff V \nsubseteq \Phi(X_S) \text{ or }W \nsupseteq \Phi(S^X).$$
\end{lemma}
\begin{proof}
$\Leftarrow$: without lose of generation suppose $V \nsubseteq \Phi(X_S)$, then
$$V \nsubseteq \Phi(X_S) \iff [\Phi(S),\Phi(X)/V ]^1=0 \Rightarrow  [W,\Phi(X)/V ]^1=0.$$

\hspace{0.8cm}$\Rightarrow$: If not, then $V \subseteq \Phi(X_S) \text{ and }W \supseteq \Phi(S^X)$, and\footnote{$[S^X,X/X_S]^1=1$ follows from \cite[Lemma 31(5)]{irelli2019cell}} 
$$[W,\Phi(X)/V]^1 \geqslant [\Phi(S^X),\Phi(X)/\Phi(X_S)]^1 =[S^X,X/X_S]^1=1.$$
We get the contradiction!
\end{proof}
\begin{corollary}\label{cor:img2}
When $\eta$ generates $\Ext^1(S,X)$, we have 
	$$\Img \Psi_{\dimvec{f},\dimvec{g}} = \bigg(\Grr_{\dimvec{f}}(\Phi(X)) \times \Grr_{\dimvec{g}}(\Phi(S)) \bigg) \setminus \bigg(\Grr_{\dimvec{f}}(\Phi(X_S)) \times \Grr_{\dimvec{g}-\dimv \Phi(S^X)}\left(\Phi(S/S^X)\right) \bigg)$$
\end{corollary}

\begin{lemma}
	For $(V,W) \in \Img \Psi$, the preimage of $(V,W)$ is a torsor of $\,\Hom_{R}(W,\Phi(X)/V)$. Or we could say, there is one non-canonical isomorphism
	$$\Psi^{-1}((V,W)) \cong \Hom_{R}(W,\Phi(X)/V).$$
\end{lemma}
\begin{proof}
???[pictures]

When $(V,W) \in \Img \Psi$, $\bar{\eta}$ is split, and each split morphism $\theta$ give us an element in $\Psi^{-1}((V,W))$. If we fix one split morphism $\theta_0$, then the other split morphisms are all of the form $\theta_0 + \textcolor{gray}{\iota \circ} f$ where $f \in \Hom_{R}(W,\Phi(X)/V)$(and this form is unique). So
$$\Psi^{-1}((V,W)) \cong \{ \theta: \text{ split morphism } \} \cong \Hom_{R}(W,\Phi(X)/V).$$
\end{proof}
\begin{lemma}
	For two $R$-modules $T,T'$, we have
	$$	\left< T,T'\right>_R \cong 	\left< \dimv T,\dimv T'\right>_R.$$
\end{lemma}
\begin{proof}
We construct one canonical resolution of $T$,

[??? Pictures]

by applying the functor $\Hom_R(-,T')$ to this resolution, we get
$$	\left< T,T'\right>_R \cong 	\left< \dimv T,\dimv T'\right>_R.$$
\end{proof}
\begin{proof}[{Proof of Theorem \ref{thm:main1} and \ref{thm:main2}}]
We have already computed $\Img \Psi$ in Corollary \ref{cor:img1} and \ref{cor:img2}. For the rank of the affine bundle, we have 
\begin{equation*}
\begin{aligned}
(V,W) \in \Img \Psi_{\dimvec{f},\dimvec{g}} &\Longrightarrow [W,\Phi(X)/V]^1=0\\
& \Longrightarrow [W,\Phi(X)/V]=\left< W,\Phi(X)/V\right>_R=\left< \dimvec{f},\dimv \Phi(X)-\dimvec{g}\right>_R
\end{aligned}
\end{equation*}
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Application: Dynkin Case}
Before discussing the affine paving property, let me introduce some new numerical concepts, which can be seen as the measure of the "complexity" of the representation.

Fix an \textbf{indecomposable} quiver representation $M \in \Rep(\mathbb{Q})$, we define the order of $M$ by
$$\ord(M):= \max_{i \in v(Q)} \dim_K M_i.$$
When the quiver $Q$ is of type $E$, we denote by $e \in v(Q)$ the unique vertex which is connected to three other vertices, and the number 
$$\orde(M):=\dim_K M_e=[P(e),M]$$
is equal to $\ord(M)$ unless $\orde(M)=0$.

By Theorem \ref{thm:main1}, we just need to focus on the case of indecomposable modules. The next lemma tells us, for the "easy representation", we can prove the affine paving property easily.

\begin{lemma}[{follows \cite[Lemma 2.22]{maksimau2019flag}}]
	For the representation $M \in \Rep(Q)$ satisfying $\ord(M) \leqslant 2$ and the dimension vector $\dimvec{f}$, the variety $\Grr_{\dimvec{f}}(\Phi(M))$ is either empty or is a singleton or is a direct product of some copies of $\mathbb{P}^1$.
\end{lemma}
\begin{proof}
	For each vertex $i$ of the bigger quiver, the dimension of $V_i$ is 0,1,2; then the variety $\Grr_{\dimvec{f}}(\Phi(M))$ is naturally included to a direct product of $\mathbb{P}^1$, and the information of arrows just reduce the number of $\mathbb{P}^1$(maybe to singleton or empty).
\end{proof}
\begin{corollary}[{\cite[Theorem 2.20]{maksimau2019flag}}]
	Assume that $Q$ is a Dynkin quiver of type $A$ or $D$, $M \in \Rep(Q)$ is the representation. then the Grassmannian $\Grr(\Phi(M))$ has an affine paving.
\end{corollary}
\begin{corollary}
	Assume that $Q$ is a Dynkin quiver of type $A$ or $D$, $M \in \Rep(Q)$ is the \textbf{regular quasi-simple} representation. then the Grassmannian $\Grr(\Phi(M))$ has an affine paving.
\end{corollary}
%We use rep 2 Cor 18.8.

\textbf{In the rest of this section we focus on the "difficult" indecomposable representation of $E_6,E_7,E_8$.} The idea is to design the special route for each case, and use Theorem \ref{thm:main2} in the process. Notice that even though the Auslander-Reiten quivers look quite different for different quiver(with same type), they can have the same form is we use the number $\orde(M)$ to represent the representation $M$:\footnote{Some representations $M$ are hidden when $\orde(M)=0$. In ??? the Figure ??? is called the starting functions.}

???[Pictures]

\begin{lemma}
	For every ind rep $Y$ of type $E$ with $\ord(Y)>2$, there is a minimal section mono $f:X \longrightarrow Y$.
\end{lemma}
\begin{proof}
	Just observe the Auslander-Reiten sequence. The chosen minimal section monos are represented in Figure ???. Notice that for the most time $\orde(-)$ is enough to guarantee the map to be a mono.
\end{proof}
\begin{remark}
	The condition $\ord(Y)>2$ in the lemma can not be removed.
\end{remark}
\begin{lemma}
Let $X \hookrightarrow Y$ be an minimal section mono, and $S:=Y/X$ be the quotient. Then we have the SES 
$$\eta: 0 \longrightarrow X \longrightarrow Y \longrightarrow S \longrightarrow 0$$
and the following values:

???[Table]

In particular, $S$ is indecomposable and rigid; $[S,X]^1 =1$, so $X_S$ and $S^X$ are well-defined.
\end{lemma}
\begin{proof}
We know that $[X,X]=[Y,Y]=1$ and $[X,X]^1=[Y,Y]^1=0$. By the definition of minimal section mono, we get
$[X,Y]=1, [Y,X]=0$ and $[X,Y]^1=[Y,X]^1=0$. By applying the functors $[Y,-],[-,S],[X,-],[-,X],[-Y]$ to the SES $\eta$ we get the results. 
\end{proof}
In the following two lemmas we will describe the representations $S^X$ and $X_S$ more clearly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application: Affine Case}



Task:


fillin the ???

change ind rep to indecomposable representations

change iff to if and only if

change SES LES

\bibliographystyle{plain}
\bibliography{reference}
\nocite{irelli2019cell}
\nocite{maksimau2019flag}




\end{document}




